Interpretable Neural Networks using EAGGA

### 2025-03-13 paper/main.tex
bullets conclusion

\section{Introduction}
Tabular Data
- most common type of data
- bad performance of deep learning models on tabular data, recent research suggests that heavy regularisation is necessary

@@

@@

@@

\section{Conclusion and Future Outlook}
- MO BO on group structure space possible?

>>>>

\section{Introduction}
Tabular Data
- most common type of data
- still difficult for neural networks  % TODO: reference, or better only in introduction
- recent research suggests that heavy regularisation is necessary  % TODO: reference, or better only in introduction

@@

  * unfortunately no comparison to unrestricted NN
  * would not be sensible, as NF, NI, NNM would be 1, hence hypervolume = 0, as values along 3 dimensions would be at reference point

@@

    - measures contribution of an individual to the hypervolume, i.e. difference between hypervolume of entire pareto front vs hypervolume of pareto front without
      individual $\boldsymbol\lambda$: $\text{CON}_{\mathcal{P}}(\boldsymbol\lambda)=\text{HYP}(\mathcal{P})-\text{HYP}(\mathcal{P}\setminus\{\boldsymbol\lambda\})$,
      where $\text{HYP}(\mathcal{P})$ denotes the hypervolume induced by the pareto set $\mathcal{P}$ \citep[p. 384]{10.5555/1943267.1943271}

@@

\section{Conclusion and Future Outlook}
(Conclusion)
- tabular data still difficult discipline for neural networks
- research suggests heavy regularisation to improve performance on tabular data
- EAGGA proved to be successful in making XGBoost more interpretable while keeping performance on par with unregularised XGBoost
- we extend EAGGA to neural networks to see if we can utilise the regularisation induced by it to make NNs both interpretable and performant on tabular data
- as consequence propose new architecture allowing to model equivalence relations of EAGGA
- found overall performance comparable to that of XGBoost fitted using EAGGA, which is a plus, but no outperformance

(Future Outlook)
- MO BO on group structure space possible?
